Universal Anonymous Signatures

### 2022-08-02 prism-backend/research/gsac/relationships.tex
Updating proofs.

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
          \pcif F(I,\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I,\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
      \end{align}

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,F,IL},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I,L}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. If the issuer
  gets $\yissue = 0$, rejects issuing a new credential. Otherwise, it completes
  the protocol and adds $\yissue$ to $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, we build a revocable anonymous credential as a $(\fissue^1,
\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. The \feval is
parameterized with a one-way and collision-resistant function $F$
(e.g., a cryptographic hash), a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by $V$. 
%
Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
it sets $\yeval^0 \gets \dattrs(\cred)$ and $\yeval^1 \gets V$; $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I,L},\feval^{\yeval^1},
\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
any open function. Concretely, by restricting to a system with one issuer and
one opener, one credential per user, one attribute per credential (the user
secret key)% , $\fissue^1$ issuance functions, and
% \feval functions that only use the $\yeval^1$ output -- which we denote with
% $\feval^{\yeval^1}$
.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I,L},\feval^{\yeval^1},
\finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one
credential per user, and one attribute per credential (the user secret key),
implements an MPS scheme where $F=\feval^{\yeval^1}$ and $G=\finsp^\ast$.
With these functions, the construction is essentially as in
\secref{ssec:related-models-gs}.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
is an input of \yinsp.

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn F(I,\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
      \end{align}

@@

\subsubsection{\CUASGS construction.} %
\todo{Clarify how $\fissue^{single,F,I}$ works! This is also common with other
  constructions...}
We show that the $(\fissue^{single,F,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,F,I}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. If the issuer
  gets $\yissue = 0$, rejects issuing a new credential. Otherwise, it completes
  the protocol and adds $\yissue$ to $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, we build a revocable anonymous credential as a $(\fissue^1,
\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. The \feval is
parameterized with a one-way and collision-resistant function $F$
(e.g., a cryptographic hash), a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by $V$. 
%
Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
it sets $\yeval^0 \gets \dattrs(\cred)$ and $\yeval^1 \gets V$; $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
Note that, in the $\feval^{\dattrs,F,V,L}$ function, $L$ is a sort of variable.
However, each verifier $V$ may just update its own list with some reasonable
frequency (e.g., daily), and use a pre-compiled version of
$\feval^{\dattrs,F,V,L}$ in which $L$ is actually a constant.
%
In more detail, the algorithms are as follows:

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
any open function. Concretely, by restricting to a system with one issuer and
one opener, one credential per user, one attribute per credential (the user
secret key)% , $\fissue^1$ issuance functions, and
% \feval functions that only use the $\yeval^1$ output -- which we denote with
% $\feval^{\yeval^1}$
.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one
credential per user, and one attribute per credential (the user secret key),
implements an MPS scheme where $F=\feval^{\yeval^1}$ and $G=\finsp^\ast$.
With these functions, the construction is essentially as in
\secref{ssec:related-models-gs}.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
is an input of \yinsp.
